Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-09 man/figures/correla_boot_sites.Rmd
update

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

@@

correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2) +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) +
  theme(legend.position = c(.8,.9), legend.title = element_blank())

correla_sitesSJCALH
```

```{r}
rtmax <- read.csv(here("data/rwi_climate", "rtmax_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'T max')
rtmin <- read.csv(here("data/rwi_climate", "rtmin_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'T min')
rsequia <- read.csv(here("data/rwi_climate", "rsequia_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name ='SPEI')
rprec <- read.csv(here("data/rwi_climate", "rprec_selected.csv"), header = TRUE, sep = ',') %>% mutate(v_name = 'Prec')

df <- rbind(rtmax, rtmin, rsequia, rprec)

label_var <- c("Prec" = "(a) Prec", "SPEI" = "(b) SPEI", 
               "T max" = "(c) T max", "T min" = "(d) T min")

label_site <- c("SJ" = "SJ",
                "caH" = "CA-High",
                "caL" = "CA-Low")

theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 6), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x = element_text(angle = 90, vjust = 0.3)),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
)

p_tmax <- df %>% filter(v_name == 'T max') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.4), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'bottom') + 
  ylab('Correlation') + 
  annotate("text", x = 2, y = 0.35, label = "T max", fontface =2, size = 5)

p_tmin <- df %>% filter(v_name == 'T min') %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.4, 0.6), 
                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
  scale_x_continuous(breaks = unique(df$id), labels = unique(df$month_name), position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.35, label = "T min", fontface =2, size = 5)

# prec-spei

dfspei <- df %>% 
  filter(v_name == 'SPEI') %>% 
  filter(month_name %in% c('Hydrol', 'Winter','Spring','Summer','Autumn')) %>% 
  # truquillo para poner juntas las dos graficas 
  mutate(id = id + 6)

dfprec <- df %>% filter(v_name == 'Prec')

# Joins df
dfprec_spei <- bind_rows(dfspei, dfprec)

# solucion para poner juntas prec + spei 
labelitas <- unique(dfprec_spei[c('id','month_name','v_name')])

p_prec_spei <- dfprec_spei %>% 
  ggplot(aes(x=id, y=coef, group = site)) + 
  geom_vline(xintercept=20) +
  theme_ring_climate + 
  scale_y_continuous(limits = c(-0.2, 0.8), 
                     breaks = c(-0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
  scale_x_continuous(breaks = labelitas$id, labels = labelitas$month_name, position = 'top') + 
  ylab('Correlation') +
  annotate("text", x = 2, y = 0.75, label = "Prec", fontface =2, size = 5) + 
  annotate("text", x = 23, y = 0.75, label = "SPEI", fontface =2, size = 5)

ptemperatura <- p_tmin + theme(legend.position="none") + p_tmax + theme(legend.position="bottom") + plot_layout(ncol=1)

ring_climate <- p_prec_spei + theme(legend.position="none") + ptemperatura + plot_layout(ncol=1, heights = c(2,3), tag_level = 'keep')  + plot_annotation(tag_levels = c('a','b')) & theme(plot.tag = element_text(size = 20, face = 2))

ring_climate
```

>>>>

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

@@

correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate)) + 
  geom_line(aes(colour=name_comparison), size = 1.4) + 
  theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_ribbon(aes(ymax=ci_upper, ymin=ci_lower, fill=name_comparison), alpha=0.3) + 
  scale_fill_colorblind() + 
  scale_color_colorblind() +
  theme(legend.position = c(.8,.9), 
        legend.title = element_blank(), 
        legend.text = element_text(size = 14),
        panel.grid = element_blank(), 
        axis.title = element_text(size = 14), 
        axis.text = element_text(size = 11))

correla_sitesSJCALH

```
